---
title: "循环"
author:
  - 陈冰顺
documentclass: ctexart
keywords:
  - 循环
output:
  rticles::ctex:
    fig_caption: yes
    number_sections: yes
    toc: yes
---
#循环
##Example: 1-Norm with For Statement
$$\left \| v \right \| _{1} = \sum_{i=1}^{n} \ \left | \left [ i \right ]  \right | $$
The vector has n elements. The most trivial algorithm to compute the 1-norm can
be described as follows:
- Initialize a sum value as zero.
- Add the absolute value of the first element to the sum value.
- Add the absolute value of the second element (if n > 2) to the sum value.
- ...
- Add the absolute value of the last element to the sum value.
- Return the sum value.
```{r}
onenorm_for <- function(v){
  sumvalue <- 0
  for(i in 1:length(v)){
    sumvalue <- sumvalue + abs(v[i])
  }
}

```
Calculation of 1-Norm Using For (Incorrect)
```{r}
onenorm_for2 <- function(v){
  sumvalue <- 0
  for (i in 1:length(v)) {
    sumvalue <- sumvalue + abs(v[1])##这里
  }
  return(sumvalue)
}
```
Specifically, instead of adding the absolute values of the elements in v, just the
absolute value of the first element is added for n times. Hence, the result (output) is
$$\sum_{i=1}^{n}|v[1]|=n|v[1]|$$
In this case, the loop and update operations are written correctly, but the number of
elements is fixed to 10. The programmer may be sure that the number of elements
in input vectors to be considered and handled via this program is always 10. But,
why not to make it more general without too much effort?

```{r}
##比较整齐的写法
onenorm_for3 <- function(v){
  sumvalue <- 0
  n <- length(v)
  for (i in 1:n) {
    sumvalue <- sumvalue + abs(v[i])
  }
  return(sumvalue)
}
```

```{r}
onenorm_for4 <- function(v){
  sumvalue <- abs(v[1])
  n <- length(v)
  for (i in 2:n) {
    sumvalue <- sumvalue + abs(v[i])
  }
  return(sumvalue)
}
```

## Example: 1-Norm with While Statement
```{r}
onenorm_while <- function(v){
  sumvalue <- 0
  i <- 1
  while(i <= length(v)){
    sumvalue <- sumvalue + abs(v[i])
    i <- i + 1
  }
  return(sumvalue)
}
```
Note the following specific commands due to the structure of the while statement:
- The variable i is initialized as 1 before the loop.
- In addition to the update of the variable sumvalue, the variable i is incremented inside the loop as i=i+1.

These are because the while statement indicates only a condition for stopping the
loop whereas no information is provided for the initialization or incrementation, as
opposed to the for statement, where all possible values of the variable i are clearly
defined.

```{r}
##错误
onenorm_while2 <- function(v){
  sumvalue <- 0
  i <- 1
  while(i <- length(v)){
    i <- i + 1##这里
    sumvalue <- sumvalue + abs(v[i])
  }
  return(sumvalue)
}
```
$$\|v\|_{1}=\sum_{i=2}^{n+1}|v[i]|$$

```{r}
onenorm_while3 <- function(v){
  sumvalue <- 0
  i <- 1
  while(i <= length(v)){
    sumvalue <- sumvalue + abs(v[i])
  }
  return(sumvalue)
}
```
This simple mistake leads to the famous infinite loop. Since i is not incremented,
the condition in the while statement is always satisfied. Hence, the program continues infinitely (at least in theory!), adding the absolute value of the first element
repetitively. This is a very serious problem.
